A few stickleback suffice to transport adaptive alleles to new lakes

### 2019-05-10 Stickleback_Paper.tex
Draft 5 before citations

\title{A few stickleback can transport adaptive alleles to new lakes}
\author{Jared Galloway, William A. Cresko, and Peter Ralph}
\maketitle

@@

Threespine stickleback provide a striking example of local adaptation to divergent habitats while still being connected by recurrent gene flow. These small fish occur in marine and freshwater habitats throughout the Northern Hemisphere, and in numerous cases smaller freshwater populations have been established ``de novo'' from marine colonists. Previous results show that a similar freshwater phenotype often evolves in independent populations soon after colonization using largely the same standing genetic variation, even in very distant geographic regions. But how many stickleback migrants are needed to capture a sufficient amount of standing variation to fuel adaptation? Here we use genealogical simulations to determine the levels of gene flow that best match observed patterns of allele sharing among habitats in stickleback, and to better understand how gene flow and local adaptation in large metapopulations determine the speed of adaptation and re-use of standing genetic variation. In our simulations we find that repeated adaptation uses a shared set of alleles that are maintained at low frequency by migration-selection balance in ocean populations. This process occurs over a realistic range of intermediate levels of gene flow that match previous empirical population genomic studies in stickleback. Examining these simulations more deeply reveals that low gene flow leads to slow, independent adaption to district habitats, whereas high gene flow leads to significant mutation load but an increased probability of successful population genomic scans for locally adapted alleles. We also find that the original generation of marine individuals that colonized the lakes is most often the sole source of most freshwater adapted alleles. These simulations provide deeper context for existing studies of stickleback evolutionary genomics, and provide guidance for future empirical studies in this model. More broadly, our results support existing theory of local adaptation but extend it by more completely documenting the genealogical history of adaptive alleles in a metapopulation.

@@

The canonical model for the genetics of adaptation has long been the sequential fixation of new mutations (\textbf{cite}). While it has been very useful heuristically for guiding studies in the field and lab (\textbf{cite}), this model is now rightfully understood as incomplete for many species in nature that have more complicated population structures (\textbf{cite}). In particular, empirical studies have increasingly pointed to the need to more deeply incorporate standing genetic variation (SGV) into adaptation dynamics for metapopulations inhabiting an array of habitats and experiencing diverse selective pressures while still exhibiting significant gene flow (\textbf{cite}). A growing number of empirical studies have identified instances of convergent evolution using SGV \citep{nelson2017ancient,Schrider2017,Barrett2008}. However, it is still not clear how variation in evolutionary processes - such as gene flow, recombination, selection and mutation -  can promote the maintenance and re-use of SGV, particularly during invasion and adaptation to new environments (\textbf{cite}). It is similarly unclear whether variation in these evolutionary processes can determine the genetic architecture of evolving traits via SGV. While emprical studies in the field and lab are essential, the use of simulation models of specific systems can greatly advanced our understanding of the adaptation genetic dynamics using SGV.

\plr{I like the spirit of the first paragraph, but want to totally rewrite it}
\wac{I did a little editing but Peter can still totally rewrite. Regardless, it needs to be streamlined a fair bit}

The threespine stickleback fish has provided some of the earliest data in a recent flood showing the heterogeneous nature of divergence across genomes (\textbf{cite}) and the much more extensive use of SGV than once thought (\textbf{cite}). The ancestral marine form of stickleback has given rise to millions of independently derived freshwater populations in recently de-glaciated regions around the Northern Hemisphere (\textbf{cite}). While geographic isolation often prevents direct migration among freshwater populations, they frequently evolve similar (but not exactly the same) phenotypes (\textbf{cite}). The most recent evolutionary genomic studies on stickleback document that while adaptation to freshwater can occur over decades (\textbf{cite}), the overall dynamic of local adaptation to marine and freshwater habitats has been occurring for millions of years (\textbf{cite}). Impressively, independent local adaptation of marine individuals to freshwater environments has been observed to take place in just tens of generations (\textbf{cite}). For example, in 1964 the Great Alaskan Earthquake caused an uplift of many islands and coastal regions throughout the Gulf of Alaska (\textbf{cite}). Studies of stickleback populations on uplifted Middleton Island showed that newly created freshwater ponds were invaded by the surrounding marine population of stickleback which evolved the freshwater syndrome of phenotypes in less than 50 years (\textbf{cite}). Amazingly, nearly a quarter of the genome diverged significantly in this same time but - with very little change in the rest of the genome - in a pattern that mirrored previous studies of freshwater stickleback populations thousands of years old (\textbf{cite}).

But how can evolution occur at such a rapid pace in this and other species? Waiting for new mutations to arise in each lake or pond would take much longer than the decades since the Alaskan earthquake (\textbf{cite}). Even more improbable is having divergence cluster in such similar genomic regions across independent populations. An alternative hypothesis, supported by the most recent population genomic analyses, is that the marjority of alleles important for freshwater adaptation are maintained in the marine individuals due to recurrent gene flow from freshwater back in to marine populations. In 2009 \citet{schluter2009genetics} proposed a conceptual model they termed the ``transporter hypothesis'' to describe the process of alleles benefical in freshwater populations are maintained at migration-selection balance in the larger oceanic population and thus available for subsequent adaptation into new freshwater habitats. The first clear example of the global reuse of SGV in stickleback was the gene \textit{eda} which has been shown to be an important regulator for the number of bony lateral plates (\textbf{cite}). While the low lateral plate version of this gene arose millions of years ago, it is found in much younger freshwater ponds around the Northern Hemisphere (\textbf{cite}). More recently, genome-wide haplotype analyses have provided evidence that \textit{most} regions of the genome that distinguish marine-freshwater genetic differences share this pattern \citep{nelson2017ancient}.

While this growing body of population genomic data on stickleback evolution support the transporter hypothesis, a number of questions remain. What are the actual population sizes, migration rates, and fitness differentials consistent with this hypothesis? How many differentially selected alleles exist, how many are used at any one time, and how are they arranged within the genome? A curious natural history observation undergirding many of these questions is the fact that some newly formed freshwater habitats, such as the ponds on Middleton Island, are quite small and presumably the number of initial marine migrants is few. Here we use forward simulations implementing in SLiM and incorporating linkage to model the stickleback metapopulation and address these questions. We ask how variation in amount of gene flow affects the genetic architecture of local adaptation to newly created freshwater ponds. Because we are documenting the entire genealogy of all alleles, we can determine the distribution and abundance of haplotypes across all in silico marine and freshwater populations to know the timing and proportion of potentially adaptive alleles that are actually utilized in each population. In addition, we can document how these adaptive alleles are distributed across the genomes, and as a consequence determine how this may affect the efficacy of genome scans for between-habitat differentiation. We find that only a few stickleback migrants per lake per generation are sufficient to maintain SGV in the ocean, allowing new freshwater populations can adapt in only tens of generations. We also find that continued gene flow of marine individuals into recently established lakes is not necessary for adaptation as the majority of alleles are present in the initial marine colonizers. Finally, we find that this rapid, local adaptation can only occur over an intermediate range of levels of gene flow. Low gene flow prevents variation from being transported, while high gene flow prevents local adaptation. Together these simulation findings enhance and extend the existing rich empirical work on stickleback evolutionary genomics.

\section*{Methods}

To explore these questions, we used SLiM \citep{haller2017slim,haller2018slim3} to implement forward-time simulation of populations of individuals with explicitly represented genomes in which selection acted upon a single continuous quantitative trait. The details of the model were motivated by current understanding of threespine stickleback evolutionary history and demography, and included divergent selection in the two habitats which had substantial spatial structure. Certain aspects of the model remain simplistic due to computational constraints. Possibly the most important caveat is that simulated population sizes are much smaller than the census size of the threespine stickleback populations observed in nature (see the Discussion for more on this).

@@

Simulations have two habitat types -- Marine and Freshwater -- defined by their selective pressures, each with 5,000 diploid individuals. The arrangement of these habitats, depicted in Figure~\ref{fig:Geo} roughly models a set of freshwater habitats along a stretch of coastline. The marine habitat is a continuous, one-dimensional range of length 25 units, while the freshwater habitat is divided into 25 discrete subpopulations (which we call ``lakes''), each connected to the marine habitat at regularly spaced intervals (positions $i - 1/2$ for $1 \le i \le 25$).

@@

Each individual carries two linear chromosomes, each of size $10^8$ loci. Mutations that can affect the trait under selection can occur at rate $10^{-10}$ per locus per generation in ten regions of $10^5$ loci each, spread evenly along the chromosome. Each mutation in these regions is either additive, completely recessive, or completely dominant (with equal probability). Effect sizes for these mutations are chosen randomly from an exponential distribution with mean $1/2$, either positive or negative with equal probability. Individual trait values ($x_\text{ind}$) are determined additively from the diploid genotypes. Concretely, an individual that is heterozygous and homozygous for mutations at sets of loci $H$ and $D$ respectively has trait value $x_\text{ind} = \sum_{i \in H} h_i s_i + \sum_{j \in D} s_j$, where $h_i$ and $s_i$ are the dominance coefficient and the effect size of the mutation at locus $i$. Subsequent mutations at the same locus replace the previous allele. We also used SLiM's ability to record \emph{tree sequences} \citep{haller2018treesequence} to add neutral mutations across the entire genome at a rate of $10^{-7}$ per locus per generation,  as described in \citet{kelleher2018efficient}.

@@

We use SLiM to simulate a Wright--Fisher population with non-overlapping generations and a fixed population size of 5,000 diploid individuals in each habitat. Each generation, the two parents of each new offspring are chosen proportional to their fitness (all individuals are hermaphroditic), and the contributing genomes are produced by Poisson recombination with an average of one crossover per chromosome per generation ($10^{-7}$ per locus per generation). Since the total population across \emph{all} 25 lakes is fixed at 5000, and the Wright--Fisher model assumes unrealistic global population regulation, we normalize the fitnesses of each individual such that approximately 200 offspring are generated in each lake, each generation. To do this, we divide fitness values of each freshwater individual by the mean fitness in their lake, so that the mean fitnesses of all lakes are equal before selection happens.

@@

To study how marine-derived populations adapt after colonizing newly appearing freshwater habitats, we introduce a new set of 25 lakes after 100,000 generations. These new lakes are populated with marine individuals to emulate a freshwater lake being colonized by oceanic stickleback. This creates two \emph{sets} of lakes, which along with the marine population have a total of 15,000 individuals. Since this introduction of lakes doubles the number of lake-to-marine immigrants,the probability that a new marine individual has freshwater parents is $2m$ instead of $m$.

\paragraph{Recording genealogical history}
We used SLiM's ability to record \emph{tree sequences} \citep{haller2018treesequence,Kelleher2016} to output the genealogical history of all individuals at the time of introduction of new lakes, at the time of adaptation, and at the end of the simulation. This allowed us to directly query the true origins of adaptive alleles. In addition, it allowed for much larger simulations by avoiding the computationally expensive task of simulating neutral mutations which were retroactively added to the gene trees at a rate of $10^{-7}$ per locus per generation, as described in \citet{kelleher2018efficient}.

The output tree sequence from each simulation allows us to explore the origin of the genetic basis of adaptation in the new lakes. To do this, we constructed the genealogical tree relating all extant chromosomes at each locus along the genome. Using these trees we classified each adaptive allele, in each genome in the new lakes at the time of adaptation, into four categories:

@@

To observe the impact of gene flow on selection in the new lakes, we varied the ocean--lake migration rate, $m$, across separate simulations from $5 \times 10^{-5}$ to $5 \times 10^{-1}$. Below, we often refer to these migration rates in terms of the number of migrants per lake, per generation, which we denote $M$. Since each lake contains 200 individuals, $M=200m$. Many aspects of adaptation changed substantially across this range, including the speed of adaptation, degree of sharing of adaptive alleles between lakes, and the population genetic signals left behind. At very low rates of gene flow, each new lake's population adapted almost completely independently throught \emph{de novo} mutation, which took a very long time ($\approx 20,000$ generations). At very high rates of gene flow, local adaptation was constrained by the large influx of locally maladaptive alleles \citet{bolnick2007natural}. Between these two extremes, genetic variation that allowed adaptation to freshwater habitats could move relatively easily between lakes. Perhaps surprisingly, only a few migrants per generation from the lakes to the ocean were needed to maintain sufficient genetic variation in the ocean to accelerate adaptation in new lakes.

@@

\begin{figure}
    \begin{center}
          \includegraphics{Final_Plots/Pheno_Dist.pdf}
          \caption{
            Distribution of mean trait values across generations of the simulation,
            for different migration rates.
            The dashed pink and purple lines at $\pm 10$ give the optimum phenotypes
            in the marine and freshwater environments, respectively.
        }
          \label{fig:MeanPhenotype}
    \end{center}
\end{figure}

@@

As shown in Figure~\ref{fig:MeanPhenotype}, local adaptation occurred in all simulations with the exception of the highest gene flow at which half of each population was composed of migrants. Figures \ref{fig:phenotype_time} and \ref{fig:phenotype_time_supp} show how mean trait values in freshwater and marine populations diverged over time, until the trait means were close to the optimal values in each habitat. Establishment of new alleles in the lakes is visible in the first few thousand generations of Figure \ref{fig:phenotype_time} as jumps in the mean trait value which move the trait by an amount of order 1 every few hundred generations.
%Trait variation within each population was small compared to the difference between populations.
At the lowest rate of gene flow, $M = 0.01$, differences at around 20 commonly polymorphic sites(about 10 that shift the trait in each direction) were responsible for most of the adaptive differences between freshwater and marine habitats. As expected, increasing migration rate decreased differentiation between habitats: as seen in Figure~\ref{fig:Fst}, $F_{ST}$ between marine and freshwater habitats at neutral sites steadily declines as migration increases.

\begin{figure}
    \begin{center}
        \includegraphics[width=\textwidth]{Final_Plots/Fst_Genome_faa.pdf}
          \caption{
        Average $F_{ST}$ in windows of 500Mb between:
        \textbf{(top)} marine habitat and old lakes;
        \textbf{(middle)} marine habitat and new lakes; and
        \textbf{(bottom)} old and new lakes.
        Each plot shows $F_{ST}$ values for a separate simulation,
        with columns corresponding to increasing gene flow from left to right.
        $F_{st}$ is calculated between all marine individuals, and all lakes pooled together.
        All locations of pre-existing freshwater adapted alleles have been highlighted by 
        pink dashed vertical lines with an alpha value of 0.3, so darker shades of pink imply more 
        freshwater adapted alleles at that location.
     } \label{fig:Fst}
    \end{center}
\end{figure}

@@

The numbers in Figure~\ref{fig:MPFAI} suggest that the dramatic increase in speed of local adaptation we observed above occurs because higher gene flow between populations allows sharing of freshwater alleles between populations.

%however, it is not enough for the marine population to hold bits and peices from independently formed haplotypes,
%For selection to act on SGV on the scale we observe in nature, the gene flow 
%initial generation to be able to rebuild

We confirmed this by using recorded tree sequences to identify the origin of each trait-affecting allele in each individual in the new lakes, as defined in the Methods. Figure~\ref{fig:Origin} shows that at the lowest rate of gene flow the majority of adaptive alleles are derived from \emph{``de novo''} mutation. As gene flow increases, a larger fraction of adaptive alleles derive from pre-existing variation in the marine population at the time of introduction. In other words, greater mixing at higher migration rates allows lakes to share alleles instead of developing their own genetic basis of adaptation.

@@

While increased migration allows sharing of adaptive alleles between lakes, at $m = 10.0$ the constant influx of alleles between the habitats creates substantial migration load. The rate at which migration load becomes substantial, 10 migrants per lake per generation, only replaces 5\% of each population each generation with migrants from the other habitat, but this is sufficient to shift the mean trait values to nearly half their optimal values, as seen in Figure \ref{fig:MeanPhenotype}.

@@

%%%%%%%%%%%%%%%%%%%%
\section*{Summary}

In this paper, we have described a realistic simulation model of a coastal meta-population to observe the effects of selection of genetic variation (SGV) across a wide range of gene flow rates.
We have shown that historical introgression, at our given parameter sets, is able to reproduce rapid and parallel adaptation similar to what we've seen in real populations such as Middleton island. 
Selection is able to rebuild the freshwater haplotype at a rapid pace (in tens of generations) from marine populations as a medium between all freshwater populations. 
Almost all rates of migration were helpful in the efficiency of the population to locally adapt except for the highest at which migration load limited the ability of the populations to reach the local optimum.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage
\appendix
\setcounter{table}{0}
\renewcommand{\thetable}{S\arabic{table}}
\setcounter{figure}{0}
\renewcommand{\thefigure}{S\arabic{figure}}

>>>>

\title{A few stickleback suffice to transport adaptive alleles to new lakes}
\author{Jared Galloway, William A. Cresko, and Peter Ralph}
\maketitle
\jgg{To me, this title makes it sound like only a "select few" stickleback have the ability to transport, no?}

@@

Threespine stickleback provide a striking example of local adaptation to divergent habitats while still being connected by recurrent gene flow. 
These small fish occur in marine and freshwater habitats throughout the Northern Hemisphere, and in numerous cases the smaller freshwater populations have been established ``de novo'' from marine colonists. 
Previous results have found similar phenotypes, between independently evolved freshwater populations, are derived largely from the same standing genetic variants found to be Identical-by-decent
Geographic isolation preventing direct migration between the freshwater populations strongly suggests that these shared adaptive alleles are transported through hybridization events with the wide-spanning marine population which acts as a medium for most freshwater populations.
However, it is still largely unknown how gene flow, recombination, and selection jointly impact standing variation to fuel adaptation.
Here we use genealogical simulations to determine the levels of gene flow that best match observed patterns of allele sharing among habitats in stickleback, and to better understand how gene flow and local adaptation in large metapopulations determine the speed of adaptation and re-use of standing genetic variation. 
In our simulations we find that repeated adaptation uses a shared set of alleles that are maintained at low frequency by migration-selection balance in oceanic populations. 
This process occurs over a realistic range of intermediate levels of gene flow that match previous empirical population genomic studies in stickleback. 
Examining these simulations more deeply reveals that lower levels of gene flow leads to slow, independent adaptation to district habitats, whereas higher levels gene flow leads to significant mutation load, but an increased probability of successful population genomic scans for locally adapted alleles. 
Surprisingly, we find that the genealogical origins of most freshwater adapted alleles can be traced back to the original generation of marine individuals that colonized the lakes, as opposed to subsequent migrants. 
These simulations provide deeper context for existing studies of stickleback evolutionary genomics, and provide guidance for future empirical studies in this model.
More broadly, our results support existing theory of local adaptation but extend it by more completely documenting the genealogical history of adaptive alleles in a metapopulation.  
\jgg{Is this intro too stickleback-y?}

@@

The canonical model for the genetics of adaptation has long been the sequential fixation of new mutations (\textbf{cite}). 
While it has proved to be a useful baseline for understanding the genetic variation we see in species today (\textbf{cite}), this model is now rightfully understood as incomplete for many species in nature that have more complicated population structures (\textbf{cite}). 
In particular, empirical studies have increasingly identified the need to more deeply incorporate standing genetic variation (SGV) into adaptation dynamics for metapopulations inhabiting an array of habitats. Populations experiencing diverse selective pressures while still exhibiting significant gene flow often result in more complex genomic signals that are still not fully understood (\textbf{cite}). 
A growing number of empirical studies have identified instances of convergent evolution using SGV \citep{nelson2017ancient,Schrider2017,Barrett2008}. 
However, it is still not clear how variation in evolutionary processes - such as gene flow, recombination, selection and mutation -  can promote the maintenance and re-use of SGV, particularly during colonization and adaptation to new environments (\textbf{cite}). 
It is similarly unclear whether variation in these evolutionary processes can determine the genetic architecture of evolving traits via SGV. 
While empirical studies in the field and lab are essential, modeling specific systems can help us understand the nature of standing genetic variants to fuel local adaptation as well as the genomic signals we can expect to see.
% of the adaptation genetic dynamics using SGV.
%\plr{I like the spirit of the first paragraph, but want to totally rewrite it}
%\wac{I did a little editing but Peter can still totally rewrite. Regardless, it needs to be streamlined a fair bit}

The ancestral marine form of threespine stickleback fish has given rise to millions of independently derived freshwater populations in recently de-glaciated regions around the Northern Hemisphere (\textbf{cite}). 
This model organism has provided some of the earliest data in a recent flood showing the heterogeneous nature of divergence across genomes (\textbf{cite}) and the much more extensive use of SGV than once thought (\textbf{cite}). 
%The ancestral marine form of threespine stickleback has given rise to millions of independently derived freshwater populations in recently de-glaciated regions around the Northern Hemisphere (\textbf{cite}). 
While geographic isolation often prevents direct migration between freshwater populations, they frequently evolve similar phenotypes (\textbf{cite}). 
The most recent evolutionary genomic studies on stickleback document that while the overall dynamic of local adaptation to marine and freshwater habitats has been occurring for millions of years (\textbf{cite}), independent local adaptation of marine individuals to freshwater environments has been observed to take place in just tens of generations (\textbf{cite}). 
For example, in 1964 the Great Alaskan Earthquake caused an uplift of many islands and coastal regions throughout the Gulf of Alaska (\textbf{cite}). 
Studies of stickleback populations on uplifted Middleton Island showed that newly created freshwater ponds were invaded by the surrounding marine population of stickleback which evolved the freshwater syndrome of phenotypes in less than 50 years (\textbf{cite}). 
Amazingly, nearly a quarter of the genome diverged significantly in this same time but - with very little change in the rest of the genome - in a pattern that mirrored previous genomic studies of freshwater stickleback populations that have been geographically separated for thousands of years (\textbf{cite}).

But how can evolution occur at such a rapid pace?
Waiting for new mutations to arise in each lake or pond would take much longer than the decades since the Alaskan earthquake (\textbf{cite}). 
Even more improbable is having divergence cluster in such similar genomic regions across independent populations. 
An alternative hypothesis, supported by the most recent population genomic analyses, is that the majority of alleles important for freshwater adaptation are maintained in the marine individuals due to recurrent gene flow from freshwater back in to marine populations. 
In 2009 \citet{schluter2009genetics} proposed a conceptual model they termed the ``transporter''- hypothesis to describe the process of alleles beneficial in freshwater environment being maintained at migration-selection balance in the larger oceanic population and thus available for subsequent adaptation to new freshwater habitats.
The first clear example of the global reuse of SGV in stickleback was the gene \textit{eda} which has been shown to be an important regulator for the number of bony lateral plates (\textbf{cite}). 
While the low lateral plate version of this gene arose millions of years ago, it is found in much younger freshwater ponds around the Northern Hemisphere (\textbf{cite}). 
More recently, genome-wide haplotype analyses have provided evidence that \textit{most} regions of the genome that distinguish marine-freshwater genetic differences share this pattern \citep{nelson2017ancient}.

While this growing body of population genomic data on stickleback evolution support the transporter hypothesis, a number of questions remain. 
What are the actual population sizes, migration rates, and fitness differentials consistent with this hypothesis? 
How many differentially selected alleles exist, how many are used at any one time, and how are they arranged within the genome? 
A curious natural history observation undergirding many of these questions is the fact that some newly formed freshwater habitats, such as the ponds on Middleton Island, are quite small and presumably the number of initial marine migrants is few. 
Here we use forward simulations implemented in SLiM incorporating linkage and realistic length genomes to model the stickleback metapopulation and address these questions \citep{haller2017slim,haller2018slim3}. 
We ask how variation in amount of gene flow affects the genetic architecture of local adaptation to newly created freshwater ponds.
Because we are documenting the entire genealogy of all alleles, we can determine the distribution and abundance of haplotypes across all in marine and freshwater populations to know the timing and proportion of potentially adaptive alleles that are actually utilized in each population. 
In addition, we can document how these adaptive alleles are distributed across the genomes, and as a consequence determine how this may affect the efficacy of genome scans for between-habitat differentiation. 
We find that only a few stickleback migrants per lake per generation are sufficient to maintain SGV in the ocean, allowing new freshwater populations can adapt in only tens of generations. 
We also find that continued gene flow of marine individuals into recently established lakes is not necessary for adaptation as the majority of alleles are present in the initial marine colonizers. 
Finally, we find that this rapid, local adaptation can only occur over an intermediate range of levels of gene flow. Low gene flow prevents variation from being transported, while high gene flow prevents local adaptation. 
Together these simulation findings enhance and extend the existing rich empirical work on stickleback evolutionary genomics.

\section*{Methods}
\jgg{Any thoughts on putting Methods after results?}

To explore these questions, we used SLiM \citep{haller2017slim,haller2018slim3} to implement complex forward-time simulation of populations of individuals with explicitly represented genomes in which selection acted upon a single continuous quantitative trait. 
The details of the model were motivated by current understanding of threespine stickleback evolutionary history and demography, and included divergent selection in the two habitats which had substantial spatial structure. 
Certain aspects of the model remain simplistic due to computational constraints.
Possibly the most important caveat is that simulated population sizes are much smaller than the census size of the threespine stickleback populations observed in nature (see the Discussion for more on this).
\jgg{I don't know where we should talk about our small population sizes ... Is this even worth mentioning here?}

@@

Our simulations have two habitat types -- Marine and Freshwater -- defined by their selective pressures, each with 5,000 diploid individuals. 
The arrangement of these habitats, depicted in Figure~\ref{fig:Geo} roughly models a set of freshwater habitats along a stretch of coastline. 
The marine habitat is a continuous, one-dimensional range of length 25 units, while the freshwater habitat is divided into 25 discrete subpopulations (which we call ``lakes''), each connected to the marine habitat at regularly spaced intervals (positions $i - 1/2$ for $1 \le i \le 25$).

@@

Each individual carries two linear chromosomes, each of size $10^8$ loci. 
Mutations that can affect the trait under selection can occur at rate $10^{-10}$ per locus per generation in ten regions of $10^5$ loci each, spread evenly along the chromosome. 
Each mutation in these regions is either additive, completely recessive, or completely dominant (with equal probability). 
Effect sizes for these mutations are chosen randomly from an exponential distribution with mean $1/2$, either positive or negative with equal probability. 
Individual trait values ($x_\text{ind}$) are determined additively from the diploid genotypes. 
Concretely, an individual that is heterozygous and homozygous for mutations at sets of loci $H$ and $D$ respectively has trait value $x_\text{ind} = \sum_{i \in H} h_i s_i + \sum_{j \in D} s_j$, where $h_i$ and $s_i$ are the dominance coefficient and the effect size of the mutation at locus $i$. Subsequent mutations at the same locus replace the previous allele. 
%We also used SLiM's ability to record \emph{tree sequences} \citep{haller2018treesequence} to add neutral mutations across the entire genome at a rate of $10^{-8}$ per locus per generation,  as described in \citet{kelleher2018efficient}.

@@

We use SLiM to simulate a Wright--Fisher population with non-overlapping generations and a fixed population size of 5,000 diploid individuals in each habitat. 
Each generation, the two parents of each new offspring are chosen proportional to their fitness (all individuals are hermaphroditic), and the contributing genomes are produced by Poisson recombination with an average of one crossover per chromosome per generation ($10^{-8}$ per locus per generation). 
Since the total population across \emph{all} 25 lakes is fixed at 5000, and the Wright--Fisher model assumes unrealistic global population regulation, we normalize the fitnesses of each individual such that approximately 200 offspring are generated in each lake, each generation. To do this, we divide fitness values of each freshwater individual by the mean fitness in their lake, so that the mean fitnesses of all lakes are equal before selection happens.

@@

To study how marine-derived populations adapt after colonizing newly appearing freshwater habitats, we introduce a new set of 25 lakes after 100,000 generations. 
These new lakes are populated with marine individuals to emulate a freshwater lake being colonized by oceanic stickleback. 
This creates two \emph{sets} of lakes, which along with the marine population have a total of 15,000 individuals. Since this introduction of lakes doubles the number of lake-to-marine immigrants, the probability that a new marine individual has freshwater parents is $2m$ instead of $m$.

\paragraph{Recording genealogical history}
We used SLiM's ability to record \emph{tree sequences} \citep{haller2018treesequence,Kelleher2016} to output the genealogical history of all individuals at the time of introduction of new lakes, at the time of adaptation, and at the end of the simulation. This allowed us to directly query the true origins of adaptive alleles. 
In addition, it allowed for much larger simulations by avoiding the computationally expensive task of simulating neutral mutations which were retroactively added to the gene trees at a rate of $10^{-8}$ per locus per generation, as described in \citet{kelleher2018efficient}.
The output tree sequence from each simulation allows us to explore the origin of the genetic basis of adaptation in the new lakes. 
To do this, we constructed the genealogical tree relating all extant chromosomes at each locus along the genome. 
Using these trees we classified each adaptive allele, in each genome in the new lakes at the time of adaptation, into four categories:

@@

To observe the impact of gene flow on selection in the new lakes, we varied the ocean--lake migration rate, $m$, across separate simulations from $5 \times 10^{-5}$ to $5 \times 10^{-1}$. 
Below, we often refer to these migration rates in terms of the number of migrants per lake, per generation, which we denote $M$. Since each lake contains 200 individuals, $M=200m$. 
Many aspects of adaptation changed substantially across this range, including the speed of adaptation, degree of sharing of adaptive alleles between lakes, and the population genetic signals left behind. 
At very low rates of gene flow, each new lake's population adapted almost completely independently through \emph{de novo} mutation, which took a very long time ($\approx 20,000$ generations). 
At very high rates of gene flow, local adaptation was constrained by the large influx of locally maladaptive alleles \citet{bolnick2007natural}. 
Between these two extremes, genetic variation that allowed adaptation to freshwater habitats could move relatively easily between lakes. 
Perhaps surprisingly, only a few migrants per generation from the lakes to the ocean were needed to maintain sufficient genetic variation in the ocean to dramatically accelerate adaptation in new lakes.

@@

\begin{figure}
    \begin{center}
          \includegraphics{Final_Plots/Pheno_Dist.pdf}
          \caption{
            Distribution of mean individual trait values across generations of the simulation,
            for different migration rates.
            The dashed pink and purple lines at $\pm 10$ give the optimum phenotypes
            in the marine and freshwater environments, respectively.
        }
          \label{fig:MeanPhenotype}
    \end{center}
\end{figure}

@@

As shown in Figure~\ref{fig:MeanPhenotype}, local adaptation occurred in all simulations with the exception of the highest gene flow at which half of each population was composed of migrants. 
Figures \ref{fig:phenotype_time} and \ref{fig:phenotype_time_supp} show how mean trait values in freshwater and marine populations diverged over time, until the trait means were close to the optimal values in each habitat. 
Establishment of new alleles in the lakes is visible in the first few thousand generations of Figure \ref{fig:phenotype_time} as jumps in the mean trait value which move the trait by an amount of order 1 every few hundred generations.
At the lowest rate of gene flow, $M = 0.01$, differences at around 20 commonly polymorphic sites(about 10 that shift the trait in each direction) were responsible for most of the adaptive differences between freshwater and marine habitats. 
As expected, increasing migration rate decreased differentiation between habitats: as seen in Figure~\ref{fig:Fst}, $F_{ST}$ between marine and freshwater habitats at neutral sites steadily declines as migration increases.

\begin{figure}
    \begin{center}
        \includegraphics[width=\textwidth]{Final_Plots/Fst_Genome_faa.pdf}
          \caption{
        Average $F_{ST}$ in windows of 500Mb between:
        \textbf{(top)} marine habitat and old lakes;
        \textbf{(middle)} marine habitat and new lakes; and
        \textbf{(bottom)} old and new lakes.
        Each plot shows $F_{ST}$ values for a separate simulation,
        with columns corresponding to increasing gene flow from left to right.
        $F_{ST}$ is calculated between all marine individuals, and all lakes pooled together.
        All locations of pre-existing freshwater adapted alleles have been highlighted by 
        pink dashed vertical lines with an alpha value of 0.3, so darker shades of pink imply more 
        freshwater adapted alleles at that location.
     } \label{fig:Fst}
    \end{center}
\end{figure}

@@

The numbers in Figure~\ref{fig:MPFAI} suggest that the dramatic increase in speed of local adaptation we observed above occurs because higher gene flow between populations allows sharing of freshwater alleles between populations.
We confirmed this by using recorded tree sequences to identify the origin of each trait-affecting allele in each individual in the new lakes, as defined in the Methods. 
Figure~\ref{fig:Origin} shows that at the lowest rate of gene flow the majority of adaptive alleles are derived from \emph{``de novo''} mutation. As gene flow increases, a larger fraction of adaptive alleles derive from pre-existing variation in the marine population at the time of introduction. In other words, greater mixing at higher migration rates allows lakes to share alleles instead of developing their own genetic basis of adaptation.

@@

While increased migration allows sharing of adaptive alleles between lakes, at $m = 10.0$ the constant influx of alleles between the habitats creates substantial migration load. The rate at which migration load becomes substantial, 10 migrants per lake per generation, only replaces 5\% of each population each generation with migrants from the other habitat, but this is sufficient to shift the mean trait values to nearly half their optimal values, as seen in Figure \ref{fig:MeanPhenotype}. 
These results present the sensitivity of a population to the amount of gene flow it experiences from neighboring species.
In our simulations, the continued gene flow from freshwater populations meant that the alleles were maintained at a constant rate with fixed demographics. 
However, future modeling efforts must be made to understand what population sizes, demographics, and evolutionary histories impact an ancestral population's capacity for carrying maladaptive alleles in its opposing environment, as well as what role a haplotype's genomic architecture play it to be rebuilt in a novel environment.

@@

\section*{Conclution}

In this paper, we have described a realistic simulation model of a coastal meta-population to observe the effects of selection on genetic variation across a wide range of gene flow rates.
We have shown that historical introgression, at our given parameter sets, is able to reproduce rapid and parallel adaptation similar to what we've seen in real populations such as Middleton island. 
Selection is able to rebuild the freshwater haplotype at a rapid pace (in tens of generations) from marine populations as a medium between all freshwater populations. 
Almost all rates of migration were helpful in the efficiency of the population to locally adapt except for the highest at which migration load limited the ability of the populations to reach the local optimum. 
We find that, after local adaptation in new lakes, the majority of adaptive variant's genealogy can be traced back to the original generation as opposed to post-colonization migrant alleles.
Additionally, quantifying the inference power of $F_{ST}$ genomic scans has revealed that higher rates of gene flow are generally more useful for identifying 
Perhaps the most notable finding is that the large marine population was able to harbor and distribute deleterious alleles to the surrounding freshwater populations with only a few migrants per population, per generation.

\jgg{This feels awkward, help please.}
%This is evidence that standing genetic variation from gene flow likely plays a key role in local adaptation for many sub-species.

\clearpage
\appendix
\setcounter{table}{0}
\renewcommand{\thetable}{S\arabic{table}}
\setcounter{figure}{0}
\renewcommand{\thefigure}{S\arabic{figure}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Below is some content that may be useful, but we can delete once the manuscript is finalized.

% Discussion

@@

% Theoretical expectations.
